%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Name:        hyperlink.tex
%% Purpose:     wxHyperLink documentation
%% Author:      Otto Wyss
%% Modified by:
%% Created:     25.4.2004
%% RCS-ID:      $Id$
%% Copyright:   (c) 2004 wxCode
%% License:     wxWindows
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{\class{wxHyperLink}}\label{wxhyperlink}

This class contains a static text element which links to an URL. Clicking on
the URL activates the standard browser (via mimetype) and opens the URL. No 
checks on the URL is done.

\wxheading{Derived from}

\helpref{wxStaticText}{wxstatictext}

\wxheading{Include files}

<wx/hyperlink.h>

\membersection{wxHyperLink::wxHyperLink}\label{wxhyperlinkconstr}

\func{}{wxHyperLink}{\void}

Default constructor.

\func{}{wxHyperLink}{\param{wxWindow*}{ parent}, \param{wxWindowID}{ id = -1},\rtfsp
\param{const wxPoint\&}{ pos = wxDefaultPosition}, \param{const wxSize\&}{ size = wxDefaultSize},\rtfsp
\param{long}{ style}, \param{const wxString\& }{name = ``hyperlink"}}

Constructor, creating and showing a hyperlink. Parameters see \helpref{Create}{wxhyperlinkcreate}.


\func{}{Create}{\param{wxWindow*}{ parent}, \param{wxWindowID}{ id = -1},\rtfsp
\param{const wxPoint\&}{ pos = wxDefaultPosition}, \param{const wxSize\&}{ size = wxDefaultSize},\rtfsp
\param{long}{ style}, \param{const wxString\& }{name = ``hyperlink"}}

Creating and showing a hyperlink.

\wxheading{Parameters}

\docparam{parent}{Parent window. Must not be NULL.}

\docparam{id}{Window identifier. A value of -1 indicates a default value.}

\docparam{pos}{Window position.}

\docparam{size}{Window size. If the default size (-1, -1) is specified then the window is sized
appropriately.}

\docparam{style}{Window style. See \helpref{wxWindow}{wxwindow}.}

\docparam{name}{Window name.}


\membersection{wxHyperLink::GetHoverCursor}\label{wxhyperlinkgethovercursor}

\constfunc{wxCursor}{GetHoverCursor}{\void}

Returns the hover cursor image.

See also \helpref{SetHoverCursor}{wxhyperlinksethovercursor}.


\membersection{wxHyperLink::SetHoverCursor}\label{wxhyperlinksethovercursor}

\func{void}{SetHoverCursor}{\param{wxCursor}{ cursor}}

Sets the hover cursor image.

See also \helpref{GetHoverCursor}{wxhyperlinkgethovercursor}.


\membersection{wxHyperLink::GetMarkedColour}\label{wxhyperlinkgetmarkedcolour}

\constfunc{wxColour}{GetMarkedColour}{\void}

Returns the marked colour.

See also \helpref{SetMarkedColour}{wxhyperlinksetmarkedcolour}.


\membersection{wxHyperLink::SetMarkedColour}\label{wxhyperlinksetmarkedcolour}

\func{void}{SetMarkedColour}{\param{wxColour}{ colour}}

Sets the marked colour.

See also \helpref{GetMarkedColour}{wxhyperlinkgetmarkedcolour}.


\membersection{wxHyperLink::GetNormalColour}\label{wxhyperlinkgetnormalcolour}

\constfunc{wxColour}{GetNormalColour}{\void}

Returns the normal colour.

See also \helpref{SetNormalColour}{wxhyperlinksetnormalcolour}.


\membersection{wxHyperLink::SetNormalColour}\label{wxhyperlinksetnormalcolour}

\func{void}{SetNormalColour}{\param{wxColour}{ colour}}

Sets the normal colour.

See also \helpref{GetNormalColour}{wxhyperlinkgetnormalcolour}.


\membersection{wxHyperLink::GetVisitedColour}\label{wxhyperlinkgetvisitedcolour}

\constfunc{wxColour}{GetVisitedColour}{\void}

Returns the visited colour.

See also \helpref{SetVisitedColour}{wxhyperlinksetvisitedcolour}.


\membersection{wxHyperLink::SetVisitedColour}\label{wxhyperlinksetvisitedcolour}

\func{void}{SetVisitedColour}{\param{wxColour}{ colour}}

Sets the visited colour.

See also \helpref{GetVisitedColour}{wxhyperlinkgetvisitedcolour}.


\membersection{wxHyperLink::GetURL}\label{wxhyperlinkgeturl}

\constfunc{wxString}{GetURL}{\void}

Returns the URL.

See also \helpref{SetURL}{wxhyperlinkseturl}.


\membersection{wxHyperLink::SetURL}\label{wxhyperlinkseturl}

\func{void}{SetURL}{\param{wxString\&}{ url}}

Sets the URL.

See also \helpref{GetURL}{wxhyperlinkgeturl}.

